WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-08 Thesis.tex
v5.1.1
Separate appendix: v5.1.2
code listing - single space and avoid span over pages

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage{biblatex}

@@

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{code-style}{
  backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,
  breaklines=true,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2,
  framesep=0pt
}
\lstset{style=code-style}

@@

% \import{results/}{sec_2-workload.tex}

% \import{results/}{sec_3-observations.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \appendix
% \import{Appendix/}{app_1_soa_and_actor_model.tex}

\graphicspath{ {./images/} }
\input{glossary.tex}
% \bibliographystyle{plain}
% \addbibresource{mendeley.bib}
\printbibliography[title={References}]
\end{document}

>>>>

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage{biblatex}
\usepackage[titletoc]{appendix}

@@

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{code-style}{
  backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
  basicstyle=\linespread{1.0}\ttfamily\footnotesize,
  breakatwhitespace=false,
  breaklines=true,
  keepspaces=true,
  numbers=left,
  numbersep=5pt,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=2,
  framesep=0pt
}
\lstset{style=code-style}

@@

\import{results/}{sec_2-workload.tex}

\import{results/}{sec_3-observations.tex}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\graphicspath{ {./images/} }
\input{glossary.tex}
% \bibliographystyle{plain}
% \addbibresource{mendeley.bib}

\addcontentsline{toc}{chapter}{References} 
\printbibliography[title={References}]

\begin{appendices}
\input{Appendix/apx_1_rest_api}
\end{appendices}

\begin{appendices}
\input{Appendix/apx_2_query_api}
\end{appendices}

\end{document}

### 2020-05-08 summary/sec_1-conclusions.tex
Make geo- consistent
code listing - single space and avoid span over pages

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice follows the concept of smart endpoints dumb pipes[?] and does specific operations that are related to the data format that responsible for handling.
\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}

>>>>

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes} and does specific operations that are related to the data format that responsible for handling.
\dbc{Need to explain the solution based on microservices as it's the most important. Also, a reference is missing here}
